Renal 1

### 2017-05-28 renal1.rmd
updated to helen healy's lectures

3 cell populations in glomerulus = {endothelial, mesangial cells, epithelial cells (foot processes and parietal), } + 2 structural units = {basement membrane, mesangium}

@@

-  Normal constituents of the glomerulus (e.g. Goodpastures syndrome; type II hypersensitivity)
-  Non-renal self antigens localised in globermuli => immune attack (e.g. SLE)
-  Exogenous antigens that localise in glomerular capillaries (e.g. PSGN)

@@

-  Blood (haemoglobin): test using urine microscopy/urinalysis = {ketones, villirubin / microscopy looks at RBCs, WBCs, epithelial cells {suggestive of non-midstream catch:not clean sample)} or urine dipstick test {protein (kidney disesae), pH, RBCs, leukocytes (WBCs), ketones(Diabetic Ketoacidosis; ketosis), specific gravity (osmolites/electrolytes in the urine), glucose (diabetes), bilirubin (cholestasis [nothing moving from gallbladder => spill into bloodstream]), nitrites (bacterial waste products)}
-  Beetroot/foods
-  Dehydration
-  Drugs/medications
-  Myoglobin
-  Menstruation
-  Porphyrins
-  Urobulinogen
-  Cholestasis: bile duct obstruction so it goes through the river (also has pale stools)

@@

-  If pain => SOCRATES; ever had before
-  Fam Hx
-  Falls/trauma
-  Sexual Hx
-  Ever had before
-  Fam Hx

@@

## Trigger 1`

Glomerulonapathies:

-  Renal cause CVS: Decrease GFR => fluid retention => overloading the heart
-  CVS causing renal: vasculitis/renal artery stenosis => kidney failure => fluid retention => overloading the heart

@@

Glomerular damage => breach in the filtration system => heavy proteinuria.

@@

DVT and kidney fn: nephrotic syndrome => losing proteins such as clotting factors (loses anti-thrombotic, loses pro-thrombotic but loses more anti-thrombotic due to the number?!) => hypercoagulable state

@@

3 most common nephropathies for nephrotic syndrome

-  minimal change (children; bowmans space epithelial cells loses its negative charge, so not much morphological change)
-  Membranous glomerulonephritis:
-  Focal segmental glomerulosclerosis (FSGS):

@@

Post infectious GN: circulating immune complexes form and clog up the glomeruli => inflamm response => damaged glomerular tufts => nephritic syndrome

>>>>

3 cell populations in glomerulus = {endothelial, mesangial cells, epithelial cells (foot processes and parietal)} + 2 structural units = {basement membrane, mesangium}

Proliferative:

-  Endothelial cells: Post infectious GN
-  Mesangial cells: IgA nephropathy
-  Parietal epithelial cells (lining bowmans capsule): crescentic GN (RPGN + nephritic syndrome)
-  GBM: Anti-GBM autoimmune response against Type IV collagen

@@

-  Normal constituents of the glomerulus (e.g. Goodpastures syndrome; type II hypersensitivity)
-  Non-renal self antigens localised in globermuli $\rightarrow$ immune attack (e.g. SLE)
-  Exogenous antigens that localise in glomerular capillaries (e.g. PSGN)

@@

-  Blood (haemoglobin): test using urine microscopy/urinalysis = {ketones, villirubin / microscopy looks at RBCs, WBCs, epithelial cells {suggestive of non-midstream catch:not clean sample)} or urine dipstick test {protein (kidney disesae), pH, RBCs, leukocytes (WBCs), ketones(Diabetic Ketoacidosis; ketosis), specific gravity (osmolites/electrolytes in the urine), glucose (diabetes), bilirubin (cholestasis [nothing moving from gallbladder $\rightarrow$ spill into bloodstream]), nitrites (bacterial waste products)}
-  Beetroot/foods
-  Dehydration
-  Drugs/medications
-  Myoglobin
-  Menstruation
-  Porphyrins
-  Urobulinogen
-  Cholestasis: bile duct obstruction so it goes through the river (also has pale stools)

@@

-  If pain $\rightarrow$ SOCRATES; ever had before
-  Fam Hx
-  Falls/trauma
-  Sexual Hx
-  Ever had before
-  Fam Hx

@@

Glomerulopathies:

-  Renal cause CVS: Decrease GFR $\rightarrow$ fluid retention $\rightarrow$ overloading the heart
-  CVS causing renal: vasculitis/renal artery stenosis $\rightarrow$ kidney failure $\rightarrow$ fluid retention $\rightarrow$ overloading the heart

@@

Glomerular damage $\rightarrow$ breach in the filtration system $\rightarrow$ heavy proteinuria.

@@

Hyperlipidaemia: lose proteins $\rightarrow$ liver detects this and compensates by producing more apolipoproteins/cholesterol  
DVT and kidney fn: nephrotic syndrome $\rightarrow$ losing proteins such as clotting factors (loses anti-thrombotic, loses pro-thrombotic but loses more anti-thrombotic due to the number?!) $\rightarrow$ hypercoagulable state (antithrombin-3 mentioned in path tute)

@@

3 most common GN for nephrotic syndrome

-  minimal change (children; bowmans space epithelial cells loses its negative charge, so not much morphological change)
-  Membranous glomerulonephritis:
-  Focal segmental glomerulosclerosis (FSGS): adults

@@

Post infectious GN: circulating immune complexes form and clog up the glomeruli $\rightarrow$ inflamm response $\rightarrow$ damaged glomerular tufts $\rightarrow$ nephritic syndrome
